\vspace{-1in} \usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{CSEC-472 Authentication Paper} \\ [14pt] \huge A Security Analysis of the Lenel BlueDiamond \\

### 2020-05-06 paper/paper/paper.tex
manually added changes from clev-dev

\subsection{Procedures}
Words

\subsection{Timeline}
Words

\subsection{Novel Techniques}
Words

\section{Preliminary Suppositions \& Implications}
Words

\subsection{Theoretical Implications}
Words

\subsection{Practical Implications}
Words

>>>>

\subsection{Procedures}
The testing performed against the readers would be broken into three primary categories: Bluetooth, RFID, and Wiegand.  These categories will follow logical attack chains to test a variety of vulnerabilites.

The Bluetooth procedures follow a primary attack chain to test for vulnerabilities.  The chain starts with either gattacker \cite{GattackingJasek} \cite{BluetoothMITMTal} or CrackLE \cite{10.1145/3190645.3190693} to gain an initial foothold.  From there, the next step is to test for either injection attacks or injection free attacks \cite{jaihc19} to clear the binding list.  After the binding list is cleared a man-in-the-middle attack can be attempted \cite{lonzetta2018security} \cite{osullivan} \cite{BluetoothMITMTal}.  From this point there are multiple attacks that can be attempted.  The first attack is to attempt to break the long-term key by brute forcing the term key \cite{sevier2019securityofble} \cite{179196}.  After this replay attacks and active sniffing can be attempted \cite{filizzola2018security} \cite{osullivan}.  Finally, the protocol could be reverse engineered to try and find vulnerabilities in the implementation.

The primary RFID attack is cloning, it is possible to try to prevent cloning though it is very hard \cite{7888545} \cite{dijkPortableBumping} \cite{mitrokotsa09} \cite{7945583}.  Secondly, the random number generator used for RFID cards can be tested for vulnerabilities \cite{6565237} \cite{mitrokotsa09}. A third possible set of attacks is to try passive and active relay against the reader \cite{hancke2009confidence} \cite{6810722}.  Another possibility is to examine the RFID card reader for possible injection attacks and remote code execution \cite{garciaIClass}.  The final attack method would be to attack the RFID chain of trust used in the reader \cite{lehtonen07}.

The Wiegand protocol attacks are relatively simple.  The first step of the attack chain is to analyze the various Wiegand outputs of the reader.  After a large enough scans have been made interception and duplication attacks can be made \cite{chung2017wiegand}. Finally, a BLEKey \cite{baseggio2015BLEKey} or similar device can be made and tested against the reader.  As a part of the Wiegand testing, attacks against the optical tamper sensor will need to be created and tested.

These three sets of attacks will cover a large amount of the reader's attack surface.  The particular kill chains are ordered to effectively build off of previous steps and to test the easier attacks before the more complicated ones.  The order also is set so that the possible dangerous attacks that could damage the device are run last.

\subsection{Timeline}
The timeline for this project assumes a eight week period for testing.  This eight week period will be broken up into five separate stages for setup, testing, and wrapup.  Eight weeks should be more than adequate to perform the necessary testing and provide a complete report.  The first period is one week long and dedicated to setup.  During this time a test lab would be built with the necessary equipment to test RFID, Bluetooth, and Wiegand.  The second period is two weeks in length and dedicated to testing RFID.  The third period is also two weeks in length, this is dedicated to testing for Bluetooth weaknesses.  The fourth period is the final two week period, this time dedicated to testing for Wiegand vulnerabilities.  The fifth and final period is one week in length, unlike the others this period is not for testing.  The last period is dedicated to writing the report to submit to Carrier for their review.

\section{Preliminary Suppositions \& Implications}
This reasearch will expand and refine on the current work available on Lenel readers and readers in general. While we could find several research papers on BLE lock examination \cite{matthewrs2017surveydoorlock}\cite{ho2016smart}\cite{ye2017security}\cite{8887393}, we found no research on readers that offer multiple protocols for communication. We have a opportunity to add insight on examining mutli-protocol readers and how to approached examining and attacking them. In addition, we could find very little on attack chains for RFID or Wiegand based attacks \cite{chung2017wiegand}. Our work will allow for the creating of a preliminary attack chain for these protocols.

\subsection{Theoretical Implications}
Existing attack chains against BLE will also be refined. We have seen these chains demonstrated \cite{lonzetta2018security}\cite{BluetoothMITMTal} already, but not laid out and explored beyond simply using the tools. These processes and procedures can be laid out and refined in this research allowing for a properly documented attack chain.

\subsection{Practical Implications}
Finally, the security of the Lenel BlueDiamond will be affirmed. Our testing will allow for third party confirmation that these devices are secure against attacks. Lenel will benefit from outsider knowledge that is not present in institutional knowledge.
